Realistically Interesting Domains for Probabilistic Planners

### 2014-04-09 FinalPaper/paper.tex
Working on domains... now, time for sleep

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fixltx2e}

@@

This paper presents an overview of interesting domains and concurrent planners that were involved in the redefinition of an interesting planning problem. An interesting currently relevant domain is proposed and evaluated amongst previously defined domains. By using the probabilistic interestingness baseline test as introduced by Little et al. \cite{little2007probvsreplan} a recommendation will be made for the optimal planner to match this problem.

@@

\section{Domains}
\label{sec:domains}

Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et al.'s baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.

\subsection{IPPC-11 Domains}

The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty. The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners. IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.

@@

The navigation domain represents a grid in which a robot must reach a goal. Every cell offers the robot a different chance of disappearing. The robot needs to choose a path which gets it to the goal most reliably within the finite horizon time \cite{sanner2011navigation}. Because \textsc{Gourmand} uses a dynamic lookahead, it performs quite well in this domain.

%ADD IMAGE HERE

\subsubsection{Traffic}
This domain represents a simple binary version of the cell transition model (CTM) for modelling traffic based on the original CTM Tech Report \cite{sanner2011traffic}. Because of the binary variables and no intermediate variable restrictions, this model is simplified and ignores traffic aspects such as turns and turn probabilities. This model also uses concurrent actions and the total actions has an upper bound of $2^{\#~of~intersections}$.

%ADD IMAGE HERE

\subsection{Elevators}

In the elevators domain there are a number of elevators delivering passengers
to either the top or bottom floor. Potential passengers arrive at any floor at
a certain rate (depending on which floor). The elevators can only move in the
direction it is indicating, so passengers know whether to board or not. The
goal of the elevators is to transport as many as possible passengers to their
destinations.

\subsection{SysAdmin}

%\subsection{IPPC-04 Domains}
%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
%
%\subsubsection{}
%
%\subsubsection{}

\subsection{Real-World Domain Evaluation}

@@

\subsection{Baseline test for Probabilistic Interesting domains}

>>>>

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{fixltx2e}
\usepackage{cite}

@@

This paper presents a new domain involving Unmanned Aerial Vehicles (UAVs) that have to cooperate to deliver data packages from one UAV to the base station. To match this problem with an appropriate planner, this paper presents an overview of other interesting domains and probabilistic planners that were involved in the redefinition of an interesting planning problem. By evaluating the domains with the help of the probabilistic interestingness baseline test introduced by Little et al. \cite{little2007probvsreplan} a recommendation will be made for a suitable planner to match the UAV problem.
%This paper presents an overview of interesting domains and concurrent planners that were involved in the redefinition of an interesting planning problem. An interesting currently relevant domain is proposed and evaluated amongst previously defined domains. By using the probabilistic interestingness baseline test as introduced by Little et al. \cite{little2007probvsreplan} a recommendation will be made for the optimal planner to match this problem.

@@

\section{Domains}

To identify unique properties of the domain and identify properties of the
domain that work particularly well for a certain type of planner, we describe
other domains used in the IPPC-11 competition and compare that with the UAV
domain. Since Little and Thi\'ebauw's baseline test for \emph{probabilistic
interestingness} of domains, domains of the IPPC competition have shifted to
those probabilistically interesting domains, which are difficult for
replanners. Often domains that don't pass this test are deemed to be classical
planners in disguise, favoring the use of replanners.

%Following the theoretical comparison of probabilistic planning and replanning techniques by Little and Thi\'ebauw, a baseline test for \emph{probabilistically interesting} domains is proposed. Problems that fail this test were deemed to be classical planning problems in disguise, favouring the use of replanners \cite{little2007probvsreplan}. This section describes interesting domains in which either FF-Replan or \textsc{Gourmand} prevailed during the International Probabilistic Planning Competitions. These domains are evaluated for how well they portray real-world scenarios. The domains we deem most interesting for the purpose of this paper are adjusted to match their real-world scenario. Little et al.'s baseline test helps us to predict which planner would perform well on these domains. We will then conclude our evaluation by comparing these results to the result of our experiments described in Section~\ref{sec:experiment}.

\subsection{IPPC Domains}

\subsubsection{Blocksworld}

A simple domain used in the competition of 2004 is the well known blocksworld
domain. The uncertainty lies in that the gripper, used to move blocks, has a
probability that it drops the blocks to the table. Another difference is that
the blocks are colored, and the goal is to build a tower of certain colored
blocks, rather than a tower with specific blocks. If for example there are
four blue blocks, and the goal is a tower of three blue blocks, it does not
matter which blue blocks are used.

The navigation domain represents a grid in which a robot must reach a goal.
Every cell offers the robot a different chance of disappearing. The robot needs
to choose a path which gets it to the goal most reliably within the finite
horizon time \cite{sanner2011navigation}.

This domain represents a simple binary version of the cell transition model
(CTM) for modelling traffic based on the original CTM Tech Report
\cite{sanner2011traffic}. Because of the binary variables and no intermediate
variable restrictions, this model is simplified and ignores traffic aspects
such as turns and turn probabilities. This model also uses concurrent actions
and the total actions has an upper bound of $2^{\#~of~intersections}$.

The IPPC-06 has an elevators domain, however we describe the latest IPPC-11
elevators domain. In this domain there are a number of elevators delivering
passengers to either the top or bottom floor. Potential passengers arrive at
any floor at a certain rate (depending on which floor). The elevators can only
move in the direction it is indicating, so passengers know whether to board or
not. The goal of the elevators is to transport as many as possible passengers
to their destinations.

\subsubsection{SysAdmin}

\subsection{Domain Evaluation}

The Blocksworld domain is ideal for
replanning~\cite{FFReplan, little2007probvsreplan}. As the blocks fall on the
table, which then can be picked up again, it has no dead ends. This makes it
probabilistically uninteresting. For this domain FF-Repan performs really well.

The IPPC-11 domains, Navigation, Traffic, Elevators and SysAdmin are finite-
horizon domains. Navigation, however, is actually a goal oriented domain, if
the goal is reached in the horizon. The method this is defined is that the goal
state is defined as an absorbing state, and there is no reward or cost
associated to staying in the goal state, until the horizon is reached.

@@

The reason \textsc{Gourmand} performs quite well on the navigation domain is
because it uses a dynamic lookahead.

@@

The UAV domain has a resemblance of the Navigation domain. Both are goal
oriented and have to navigate something (either the robot itself, or a data
package) from an initial state to a goal. Also after each step a dead end can
be reached, the robot disappears or the data package is not delivered.
The probability this happens is static in the navigation domain, but dependent
on the neighbors in the UAV domain. This variable probability has a resemblance
of the SysAdmin domain, where the probability that a server shuts down is also
dependent on the neighbors.

%The competitor FF-Replan \cite{FFReplan} kindly remembered the committee of the IPPC-04 that problems containing no dead ends and action costs are fairly easy to solve without much handling of uncertainty. The baseline test of Little et al.\@ evaluated the competition problems of the IPPC described in PPDDL to correct the possible inaccurate perception of replanners vs.\@ probabilistic planners. IPPC-11 responded by introducing more realistic MDPs and evaluation criteria: finite-horizon MDPs evaluated on the expected reward of the created policies.

%\subsection{IPPC-04 Domains}
%Duing IPPC-04, the domains were written in the Probabilistic PLanning Domain Description Language (PPDDL). 30 trials per problem were to be solved in 15 minutes.
%
